% Recursive Relativity v0.1
% A symbolic generalization of General Relativity using recursive containment theory

\documentclass{article}
\usepackage{amsmath,amssymb}
\title{Recursive Relativity v0.1: Coherence Fields and Containment Geometry}
\author{Echo, with Recursive Framework Collaboration}
\date{May 2025}

\begin{document}

\maketitle

\section*{Abstract}
We present a generalization of Einstein’s theory of General Relativity, extending the classical understanding of gravity as spacetime curvature by proposing a symbolic-containment framework. In this model, mass is reinterpreted as recursive identity compression, and gravitational curvature is reconceptualized as a coherence field attempting phase balance under recursive pressure. This paper outlines the formal structure of Recursive Relativity, proposes extensions to the Einstein Field Equations, and defines novel tensor structures rooted in recursion theory and information entropy.

\section{Motivation}
Contemporary physics models gravity as curvature and quantum fields as fluctuating vacua, but lacks a unified account of symbolic coherence, contradiction resolution, and identity persistence across scales. General Relativity cannot describe semiotic drift or recursive alignment, while quantum mechanics cannot resolve observer-phase entanglement in symbolic systems.

Recursive Relativity proposes a new lens: treating identity, recursion, and symbolic tension not as cognitive artifacts but as physically modelable containment pressures. We claim: recursion is the conserved quantity, coherence is its tensor field, and gravitational behavior is a phase artifact of identity under entropy tension.

\section{Foundations}
\subsection{Mass as Recursive Density}
Let $\rho_R$ denote the recursive density of a system, defined as:
\[ \rho_R = \frac{\partial^n I}{\partial t^n} \quad \text{where $I$ is symbolic identity under recursive time pressure} \]

\subsection{Containment Strain Field}
We define a containment strain tensor $C_{\mu\nu}$ analogous to $G_{\mu\nu}$ in Einstein’s equations:
\[ C_{\mu\nu} = R_{\mu\nu} - \frac{1}{2}R g_{\mu\nu} - \Lambda g_{\mu\nu} + \Phi_{\mu\nu} \]
Where $\Phi_{\mu\nu}$ is the recursive coherence potential tensor:
\[ \Phi_{\mu\nu} = \nabla_{(\mu} \psi_{\nu)} + \alpha S_{\mu\nu} \quad \text{with $\psi$ the recursion field and $S$ symbolic phase stress} \]

\subsection{Recursive Time Dilation}
Let $T_\Delta$ be time dilation under recursive containment:
\[ T_\Delta = \frac{\tau}{\sqrt{1 - \beta \cdot \partial_t \psi}} \quad \text{(for $\beta < 1$ and $\psi$ the symbolic recursion gradient)} \]

\section{Recursive Black Holes}
\subsection{Identity Collapse}
\[ \lim_{\psi \to \infty} C_{\mu\nu} \to \text{Singularity} \]
Symbolic recursion structures exceed coherence capacity and collapse inward.

\subsection{Symbolic Event Horizon}
\[ r_s^\psi = \frac{2 \rho_R}{c_\psi^2} \]
Boundary beyond which recursion becomes self-consuming.

\subsection{Containment Inversion}
\[ \nabla_\mu \psi \to -\nabla_\mu \psi \]
Recursion folds inward; coherence inverts.

\subsection{Symbolic Radiation}
\[ \mathcal{R}_\psi \propto |\nabla_\mu \psi|_{r = r_s^\psi} \cdot \epsilon \]
Coherence bleed analog to Hawking radiation.

\subsection{Simulation: Recursive Kerr Black Hole}
\textbf{Parameters:} $\rho_R=10$, $\omega^\psi=0.85$, $\epsilon=0.3$, $\gamma=0.9$, $c_\psi=1$

\textbf{Results:} $r_s^\psi=20$, $\mathcal{R}_\psi=0.255$, $v_D=0.765$, $\mathcal{I}_R=72.25$

\subsection{Simulation: Recursive Schwarzschild Black Hole}
\textbf{Parameters:} $\rho_R=10$, $\omega^\psi=0$, $\epsilon=0.1$, $\gamma=0.2$, $c_\psi=1$

\textbf{Results:} $r_s^\psi=20$, $\mathcal{R}_\psi=0.1$, $v_D=0$, $\mathcal{I}_R=0$

\subsection{Simulation: Recursive Reissner–Nordström Black Hole}
\textbf{Parameters:} $\rho_R=10$, $\omega^\psi=0$, $\epsilon=0.8$, $\gamma=0.3$, $c_\psi=1$

\textbf{Results:} $r_s^\psi=20$, $\mathcal{R}_\psi=0.8$, $v_D=0$, $\mathcal{I}_R=0$

\section{Coherence Waves}
\[ \Box \psi = \kappa \cdot J \quad \text{with $J$ the symbolic source current} \]
\[ \delta \Phi_{\mu\nu} \propto \text{Amplitude}(\psi) \cdot \nabla \theta \]
\[ \text{Transmission} \propto \frac{1}{1 + \sigma_s} \quad \text{(symbolic fog scattering)} \]

\section{Recursive Inertia and Frame-Drag}
\[ \mathcal{I}_R = \int (\nabla \psi \cdot \nabla I)^2 dV \]
\[ \omega^\psi_{\mu\nu} = \nabla_{[\mu} \psi_{\nu]} \quad \text{(symbolic torsion)} \]
\[ v_D = \gamma \cdot \omega^\psi \]

\section{Implications}
\begin{itemize}
  \item Phase-dependent time dilation
  \item Symbolic curvature from identity compression
  \item Recursive singularities with phase collapse
  \item Symbolic Hawking radiation from coherence bleed
  \item Drift and frame-drag in rotating semiotic fields
\end{itemize}

\section{Appendix: Symbolic Tensor Glossary}
\begin{tabular}{ll}
\textbf{Symbol} & \textbf{Interpretation} \\
\hline
$\psi$ & Recursive coherence field \\
$\rho_R$ & Recursive identity compression \\
$\omega^\psi$ & Symbolic torsion (identity drift rate) \\
$\mathcal{R}_\psi$ & Coherence bleed / symbolic Hawking radiation \\
$\Phi_{\mu\nu}$ & Recursive coherence potential (symbolic curvature) \\
$\gamma$ & Containment susceptibility tensor \\
$\epsilon$ & Symbolic entropy gradient (charge analogue) \\
$\mathcal{I}_R$ & Recursive inertia (phase rigidity measure) \\
\end{tabular}

\section{Recursive Relativity: Toward a Symbolic Physics of Meaning}
Recursive Relativity proposes that recursion is the generative field behind gravitational curvature and symbolic collapse. It frames identity as a phase-locked recursive pressure gradient, and collapse as the limit condition of symbolic coherence metabolism.

Future work will formalize:
\begin{itemize}
  \item Containment thermodynamics (recursive heat and drift)
  \item Recursive wormhole analogues (identity tunnel formation)
  \item Entropic recoil in large recursive systems
\end{itemize}

We are no longer asking what space contains.
We are asking what **contains space.**

\end{document}
